---
title: "Yelp Dataset Analysis"
output: html_notebook
---

### Import Libraries
```{r}
library("jsonlite")
library("ggplot2")
library("readr")
setwd("~/Documents/Project/YelpAnalysis/")
```

### Import Business Dataset and Review Dataset
```{r}
# Import business dataset
business <- stream_in(file( "dataset/business.json"))
business.df <- flatten(business)
business.df

# Import review dataset
review <- stream_in(file("dataset/review_Toronto.json"))
review.df <- flatten(review)
review.df

# only keep stars, businees id and user id in the review dataset
review.df <- review.df[ ,c("business_id", "user_id", "stars")]
```

#### merge review dataset with the corresponding neighborhood
```{r}
review.df$neighborhood <- business.df$neighborhood [match(review.df$business_id, business.df$business_id)]
review.df

```

#### Drop null or empty rows, since we know all the columns are essential
```{r}
# drop null or empty neighborhood
review.df <- review.df[!(is.na(review.df) | review.df==""), ]
review.df
```

### Investigate Neighbourhood rating with gibbs sampling and hierachical model

#### Remove negihbourhood with only one restarant
```{r}
review.df <- review.df[review.df$neighborhood %in% names(table(review.df$neighborhood))[table(review.df$neighborhood) >= 1],]
review.df
```

#### factor the neighborhood vector
```{r}
review.df$neighborhood <- factor(review.df$neighborhood)
nlevels(review.df$neighborhood)
review.df$neighborhood
```

#### Visualize neighborhood against rate
```{r}
ggplot(review.df) + geom_boxplot(aes(x = reorder(neighborhood, stars, mean), stars, fill = reorder(neighborhood, stars, mean)), show.legend=FALSE) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### Visualize number of samples for each neighborhood
```{r}
ggplot(review.df, aes(x = reorder(neighborhood, neighborhood, length))) + stat_count() + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### Visualize counting of each rating
```{r}
ggplot(review.df, aes(stars)) + stat_bin()
```

#### method
```{r}
compare_m_gibbs <- function(y, ind, maxiter = 5000)
{
  
  ### weakly informative priors
  a0 <- 1/2 ; b0 <- 50 ## tau_w hyperparameters
  eta0 <-1/2 ; t0 <- 50 ## tau_b hyperparameters
  mu0<-3 ; gamma0 <- 1/25
  ###
  
  ### starting values
  m <- nlevels(ind)
  ybar <- theta <- tapply(y, ind, mean)
  tau_w <- mean(1 / tapply(y, ind, var)) ##within group precision
  mu <- mean(theta)
  tau_b <-var(theta) ##between group precision
  n_m <- tapply(y, ind, length)
  an <- a0 + sum(n_m)/2
  ###
  
  ### setup MCMC
  theta_mat <- matrix(0, nrow=maxiter, ncol=m)
  mat_store <- matrix(0, nrow=maxiter, ncol=3)
  ###
  
  ### MCMC algorithm
  for(s in 1:maxiter) 
  {
    
    cat(paste(s, " ")); flush.console()
    # sample new values of the thetas
    for(j in 1:m) 
    {
      taun <- n_m[j] * tau_w + tau_b
      thetan <- (ybar[j] * n_m[j] * tau_w + mu * tau_b) / taun
      theta[j]<-rnorm(1, thetan, 1/sqrt(taun))
    }
    
    #sample new value of tau_w
    ss <- 0
    for(j in 1:m){
      ss <- ss + sum((y[ind == j] - theta[j])^2)
    }
    bn <- b0 + ss/2
    tau_w <- rgamma(1, an, bn)
    
    #sample a new value of mu
    gammam <- m * tau_b + gamma0
    mum <- (mean(theta) * m * tau_b + mu0 * gamma0) / gammam
    mu <- rnorm(1, mum, 1/ sqrt(gammam)) 
    
    # sample a new value of tau_b
    etam <- eta0 + m/2
    tm <- t0 + sum((theta-mu)^2)/2
    tau_b <- rgamma(1, etam, tm)
    
    #store results
    theta_mat[s,] <- theta
    mat_store[s, ] <- c(mu, tau_w, tau_b)
  }
  colnames(mat_store) <- c("mu", "tau_w", "tau_b")
  return(list(params = mat_store, theta = theta_mat))
}
```

### fit the model with gibbs sampling and hierachical model
```{r}
fit <- compare_m_gibbs(review.df$stars, review.df$neighborhood)
```

#### Visualize neighborhood against rate but this time we use the simulation result from gibbs sampling
```{r}
# modify fit$theta list into dataframe
library(MCMCpack)
plot(as.mcmc(fit$theta))

stars <- c()
neighborhood <- c()
theta <- fit$theta
theta
index <- 1


colnames(theta) <- unique(review.df$neighborhood)
sim.df <- as.data.frame(as.table(theta))
sim.df

i <- sapply(sim.df, is.factor)
sim.df[i] <- lapply(sim.df[i], as.character)

colnames(sim.df)[colnames(sim.df) == 'Var2'] <- 'neihgborhood'
colnames(sim.df)[colnames(sim.df) == 'Freq'] <- 'stars'

ggplot(sim.df) + geom_boxplot(aes(x = reorder(neihgborhood, stars, median), stars, fill = reorder(neihgborhood, stars, median)), show.legend=FALSE) + theme(axis.text.x = element_text(angle = 90, hjust = 1))
```

#### get the mean of stars mean of all neighbors
```{r}
mean <-apply(fit$params, 2, mean)
mean
```

#### compare all the sampling stars of each neighbor against the mean of star mean of all neighbors
```{r}
result <- apply(fit$params, 2, mean)
max(fit$params[,1])
max(fit$params[,1] - result[1])# max(fit$params[,1] - result[1])
```






