---
title: "Yelp Dataset Analysis - part2"
output: html_notebook
---

### Import Libraries
```{r}
library("jsonlite")
library("ggplot2")
library("readr")
setwd("~/Documents/Project/YelpAnalysis/")
```

### Import Business Dataset and Review Dataset
```{r}
# Import business dataset
business <- stream_in(file( "dataset/business.json"))
business.df <- flatten(business)
business.df

# Import review dataset
review <- stream_in(file("dataset/review_Toronto.json"))
review.df <- flatten(review)
review.df

# only keep stars, businees id and user id in the review dataset
review.df <- review.df[,c("business_id", "user_id", "stars")]
review.df
```

#### merge review dataset with the corresponding categories & neighborhood
```{r}
review.df$categories <- business.df$categories [match(review.df$business_id, business.df$business_id)]
review.df$neighborhood <- business.df$neighborhood [match(review.df$business_id, business.df$business_id)]
review.df
```

#### Drop null or empty rows, since we know all the columns are essential
```{r}
# drop null or empty neighborhood
review.df <- review.df[!apply(is.na(review.df) | review.df == "", 1, all),]
review.df
```

### Investigate variable correlations with MCMC regression

#### Encode all the caterogries
```{r}
# one-hot-encode all the categories
library(qdapTools)
categories <- mtabulate(review.df$categories)
categories
```

#### Encode all the neighborhoods
```{r}
# one-hot-encode all the neighborhoods
neighborhood_ = factor(review.df$neighborhood) 
neighborhood_ <- gsub(" ","_", neighborhood_)
neighborhood = as.data.frame(model.matrix(~neighborhood_)[,-1])
neighborhood
```

#### create a count dataframe to count the frequency of each unique category and then sum them, Keep the categories with the  top 15 frequency
```{r}
# drop restaurant category as all business have it
categories <- categories[ , !(names(categories) %in% c("Restaurants"))]

# create a count dataframe to count the frequency of each unique category and then sum them
categories.sum <- data.frame(
                 category=character(),
                 counts=integer(),
                 stringsAsFactors=FALSE)

for (name in names(categories)) {
  categories.sum[nrow(categories.sum) + 1,] = list(name, sum(categories[name]))
}
categories.sum

# Keep the top 15 categories
eliminated.categories <- categories.sum[order(categories.sum$counts, decreasing = TRUE),]
eliminated.categories <- eliminated.categories[1:15,]
eliminated.categories

ggplot(eliminated.categories, aes(x = category, y=counts)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab("Top 15 most frequent categories")

# remove all the column that is not the top 15 category
categories.filtered <- categories[eliminated.categories$category]
categories.filtered
```

#### create a count dataframe to count the frequency of each unique neighborhood and then sum them, Keep the categories with the  top 15 frequency
```{r}
# create a count dataframe to count the frequency of each unique category and then sum them
neighborhood.sum <- data.frame(
                 neighborhood=character(),
                 counts=integer(),
                 stringsAsFactors=FALSE)

for (name in names(neighborhood)) {
  neighborhood.sum[nrow(neighborhood.sum) + 1,] = list(name, sum(neighborhood[name]))
}
neighborhood.sum

# Keep the top 15 categories
eliminated.neighborhood <- neighborhood.sum[order(neighborhood.sum$counts, decreasing = TRUE),]
eliminated.neighborhood <- eliminated.neighborhood[1:15,]
eliminated.neighborhood

ggplot(eliminated.neighborhood, aes(x = neighborhood, y=counts)) + geom_bar(stat="identity") + theme(axis.text.x = element_text(angle = 90, hjust = 1)) + xlab("Top 15 most frequent neighbors")

# remove all the column that is not the top 15 category
neighborhood.filtered <- neighborhood[eliminated.neighborhood$neighborhood]
neighborhood.filtered
```

#### merge the categories back to business dataframe, Only keep the target column, the explanatory columns(categories column) and business id and name
```{r}
library(dplyr)
categories.filtered$ID <- seq.int(nrow(categories.filtered))
review.df$ID <- seq.int(nrow(review.df))
encoded.review.df <- left_join(review.df, categories.filtered)
encoded.review.df <- encoded.review.df[ , !(names(encoded.review.df) %in% c("categories"))]
encoded.review.df
```

#### merge the categories back to business dataframe, Only keep the target column, the explanatory columns(categories column) and business id and name
```{r}
neighborhood.filtered$ID <- seq.int(nrow(neighborhood.filtered))
encoded.review.df <- left_join(encoded.review.df, neighborhood.filtered)
encoded.review.df <- encoded.review.df[ , !(names(encoded.review.df) %in% c("neighborhood"))]
encoded.review.df
```

#### Apply MCMC Linear Regression
```{r}
library(MCMCpack)
lm <- lm(stars ~ . - ID - business_id - user_id, encoded.review.df)
step_AIC <- step(lm)
summary(step_AIC)
install.packages("arm")
library(arm)
coefplot(step_AIC)
plot(step_AIC)
step_BIC <- step(lm, k=log(nrow(encoded.review.df)))
step_BIC
plot(lm)
summary(lm)
```
#### Apply MCMC Linear Regression
```{r}
library(MCMCpack)
lm1 <- MCMCregress(stars ~ . - ID - business_id - user_id, encoded.review.df)
plot(lm1)
summary(lm1)
```
