---
title: "Yelp Dataset Analysis - part3"
output: html_notebook
---

### Import Libraries
```{r}
library("jsonlite")
library("ggplot2")
library("readr")
setwd("~/Documents/Project/YelpAnalysis/")
```

### Import Business Dataset
```{r}
business <- stream_in(file( "dataset/business_open_Toronto.json"))
business.df <- flatten(business)
business.df
```

#### remove null neighborhood rows
```{r}
business.df <- business.df[!(is.na(business.df$neighborhood) | business.df$neighborhood==""), ]
business.df
```

### Investigate Neighbourhood rating with gibbs sampling and hierachical model

#### Encode all the caterogries
```{r}
# one-hot-encode all the categories
library(qdapTools)
categories <- mtabulate(business.df$categories)
categories
```

#### create a count dataframe to count the frequency of each unique category and then sum them, Keep the categories with the  top 15 frequency
```{r}
# create a count dataframe to count the frequency of each unique category and then sum them
categories.sum <- data.frame(
                 category=character(),
                 counts=integer(),
                 stringsAsFactors=FALSE)

for (name in names(categories)) {
  categories.sum[nrow(categories.sum) + 1,] = list(name, sum(categories[name]))
}
categories.sum

# Keep the top 15 categories
eliminated.categories <- categories.sum[order(categories.sum$counts, decreasing = TRUE),]
eliminated.categories <- eliminated.categories[1:16,]
eliminated.categories

# remove all the column that is not the top 15 category
library(dplyr)
categories.filtered <- categories[eliminated.categories$category]
categories.filtered
```

#### merge the categories back to business dataframe, Only keep the target column, the explanatory columns(categories column) and business id and name
```{r}
categories.filtered$ID <- seq.int(nrow(categories.filtered))
business.df$ID <- seq.int(nrow(business.df))
encoded.business.df <- left_join(business.df[,c("ID", "neighborhood")], categories.filtered)
encoded.business.df
```

#### Remove unnecessary column (id) and label the neighborhood data
```{r}
# drop unneeded columns
drops <- c("ID", "Restaurants")
encoded.business.df <- encoded.business.df[ , !(names(encoded.business.df) %in% drops)]
encoded.business.df

# # label neighborhood
# encoded.business.df$neighborhood <- factor(encoded.business.df$neighborhood)
# encoded.business.df$neighborhood <- as.numeric(encoded.business.df$neighborhood)
# encoded.business.df
```

```{r}

ClusterNum <- list()
BIC <- list()

for(i in 1:10) {
  fit <- blca.em(encoded.business.df[, -1], i)
  ClusterNum[i-1] <- i
  BIC[i-1] <- fit$BIC
}
t_in <- do.call(rbind, Map(data.frame, ClusterNum=ClusterNum, BIC=BIC))
```

#### Apply Mixture Model to Cluster the dataset
```{r}
library(BayesLCA)

ClusterNum2 <- list()
BIC2 <- list()

for(i in 1:7) {
  fit <- blca.em(encoded.business.df[, -1], i*10)
  ClusterNum2[i-1] <- i*10
  BIC2[i-1] <- fit$BIC
  print(fit)
}

ten_val <- do.call(rbind, Map(data.frame, ClusterNum=ClusterNum2, BIC=BIC2))
ten_val
```

```{r}
fit2 <- blca.em(encoded.business.df[, -1], 7)
print(fit2)

par(mfrow = c(2,2))
plot(table(MAP(Zscore(encoded.business.df[, -1], fit2)), encoded.business.df$neighborhood), main = 'groups against neighborhoods', las = 1)
dt <- table(encoded.business.df$neighborhood, MAP(Zscore(encoded.business.df[, -1], fit2)))
dt
neighborhood_group <- as.data.frame.matrix(dt) 
neighborhood_group.df <- subset(neighborhood_group, select=c("Scarborough", "Downtown Core"))
plot(fit2, which = 1)
dt
heatmap(dt, Rowv=NA, Colv=NA, col = cm.colors(256), scale="column", margins=c(1,1))

for (row in rownames(dt)) { dt[row, ] <- dt[row, ] / sum(dt[row, ]) }
dt
```

